### 2022-03-02 sections/teaching.tex
Update teaching.tex

\begin{cventries}

\begin{itemize}
\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
\begin{itemize}
\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\item{\small Faculty of Economics and Management, {\bfseries Universidad de Santiago}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Political Science I (undergraduate lecture), Spring 2014, 2018, Fall 2015-2019}
\item[$\circ$]{\small Political Science II (undergraduate lecture), Spring 2015-2018}
\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), Fall 2018}
\item[$\circ$]{\small Workshop for Research Design (graduate seminar), Spring 2017-2018}
\item[$\circ$]{\small Research Methodology (undergraduate lecture), Spring 2014-2015, Fall 2015-2017}
\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), Fall 2017}
\end{itemize}
\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), Fall 2016}
\item[$\circ$]{\small Political Analysis (undergraduate lecture), Fall 2014}
\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), Spring 2013-2014}
\end{itemize}
\end{itemize}

\vspace{1mm}
\end{cventries}

>>>>

\begin{publications}

\begin{itemize}
\item{\small School of Business, {\bfseries Universidad Mayor}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Machine Learning in Public Policy and Economics (workshop, Prof. Carla Cisternas), Spring 2021}
\end{itemize}
\item{\small Department of Politics and International Relations, {\bfseries University of Oxford}, Oxford, UK}
\begin{itemize}
\item[$\circ$]{\small Comparative Government (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\item{\small Faculty of Adminstration and Economics, {\bfseries Universidad de Santiago}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Political Science I (undergraduate lecture), Spring 2014, 2018, Fall 2015-2019}
\item[$\circ$]{\small Political Science II (undergraduate lecture), Spring 2015-2018}
\item[$\circ$]{\small Econometrics for Public Policies (undergraduate lecture), Fall 2018}
\item[$\circ$]{\small Workshop for Research Design (graduate seminar), Spring 2017-2018}
\item[$\circ$]{\small Research Methodology (undergraduate lecture), Spring 2014-2015, Fall 2015-2017}
\item[$\circ$]{\small Introduction to Quantitative Methods (undergraduate lecture), Fall 2017}
\end{itemize}
\item{\small School of Government and Public Management, {\bfseries Universidad de Chile}, Santiago, Chile}
\begin{itemize}
\item[$\circ$]{\small Study of Political Phenomena (undergraduate lecture), Fall 2016}
\item[$\circ$]{\small Political Analysis (undergraduate lecture), Fall 2014}
\item[$\circ$]{\small Elite Theory and Democracy (undergraduate lecture, Prof. Alejandro Olivares), Spring 2013-2014}
\end{itemize}
\end{itemize}

\vspace{1mm}
\end{publications}
